Enhancing Forecast Reconciliation: A Study of Alternative Covariance Estimators

### 2025-06-23 literature/paper_draft.qmd
notations and frameworks for hirerachy

-   **Context & Motivation:**

    Hierarchical (and grouped) time series are collections of time series data connected via linear constraints (linear combinations?). Forecast reconciliation ensures that forecasts satisfy these constraints.

    One of the widely used appoarch is the MinT approach. It minimises the trace of reconciled forecast errors covariance matrix (minimum variance) and depends critically on the covariance matrix of h-step ahead base forecast errors $W_h$.

## Background

@@

where $\boldsymbol{S}$ is a summing matrix of order $n \times n_b$ which aggregates the bottom-level series $\boldsymbol{b}_t \in \mathbb{R}^{n_b}$ to the series at aggregation levels above. The $n$-vector $\boldsymbol{y}_t \in \mathbb{R}^n$ contains all observations at time $t$.

The summing matrix $\boldsymbol{S}$ for the tree structure in @fig-hierarchy is:

@@

# Methodology

## Theoretical Framework

### Hierarchical and Grouped Time Series Structure

Hierarchical/Grouped time series satisfy a set of linear constraints, often represented as: $$
\boldsymbol{y}_t = \boldsymbol{S} \boldsymbol{b}_t,
$$ where $\boldsymbol{S}$ is a summing matrix of order $m x n$ which aggregates the bottom-level series $\boldsymbol{b}_t$ ($n$-vector) to the series at aggregation levels above. The $m$-vector $\boldsymbol{y}_t$ contains all observations at time $t$

Let $\hat{y}_t(h)$ be a vector of h-step-ahead base forecasts for each time series in the collection, using information up to and including time $t$, and stacked in the same order as $y_t$. Then we can rewrite the linear reconciliation forecast equation as:

$$
\tilde{y}_t(h) = SP\hat{y}_t(h)
$$ where $P$ is an $n$x$p$ matrix that maps the base forecasts into bottom-level disaggregated forecasts $\hat{b}_t$.

-   Expand on this, include graphs, examples...

### The Minimum Trace (MinT) Reconciliation

@@

## Covariance Estimation Approaches

@@

### The Shrinkage Estimator

@@

### The NOVELIST Estimator

@@

### Alternative Covariance Estimators

>>>>

<!-- ############  Background  ############ -->

@@

@@

# Theoretical Framework

## Hierarchical tructure

where $\boldsymbol{S}$ is a summing matrix of order $n \times n_b$ which aggregates the bottom-level series $\boldsymbol{b}_t \in \mathbb{R}^{n_b}$ to the series at aggregation levels above. The vector $\boldsymbol{y}_t \in \mathbb{R}^n$ contains all observations at time $t$. The summing matrix $\boldsymbol{S}$ for the tree structure in @fig-hierarchy is:

Assume we produce $h$-step-ahead base forecasts $\hat{\boldsymbol{b}}_{t+h|t}$ for the bottom-level series, obtained by any prediction methods. Then pre-multiplying them by $\boldsymbol{S}$ we get:

$$
\tilde{\boldsymbol{y}}_{t+h|t} = \boldsymbol{S} \hat{\boldsymbol{b}}_{t+h|t} .
$$ {#eq-sb}

We refer to $\tilde{\boldsymbol{y}}_{t+h|t}$ as coherent forecasts, as they respect the aggregation structure. We also refer to this way of obtaining coherent forecasts by summing the bottom-level forecasts as the bottom-up approach. However, generating forecasts this way is anchored only to prediction models at a single level, and will not be utilising the information from other levels. This drawback applies to the top-down and middle-out approaches. For example, the bottom-level data can be very noisy or even intermittent, and the higher-level data might be smoother due to the aggregation.

Another issue with expressing reconciled methods as in @eq-sb is that it restricts the reconciliation to only single-level approaches. Thus, @Hyndman2011-jv suggested a generalised expression for all existing methods, which also provides a framework for new methods to be developed:

$$
\tilde{\boldsymbol{y}}_{t+h|t} = \boldsymbol{S} \boldsymbol{G} \hat{\boldsymbol{y}}_{t+h|t},
$$ {#eq-sgy}

for a suitable $n_b \times n$ matrix $\boldsymbol{G}$. $\boldsymbol{G}$ maps the base forecasts of all levels $\hat{\boldsymbol{y}}_{t+h|t}$ down into the bottom level, which is then aggregated to the higher levels by $\boldsymbol{S}$. The choice of $\boldsymbol{G}$ determines the composition of reconciled forecasts $\tilde{\boldsymbol{y}}_{t+h|t}$, and modern methods are developed to estimate $\boldsymbol{G}$.

<!-- including the OLS and WLS developed by @Hyndman2011-jv and @Hyndman2016-ic, respectively. A more detailed explanation of these methods can be found in the @sec-ols-wls Appendix. -->

## The Minimum Trace (MinT) Reconciliation

@@

# Covariance Estimation Approaches

@@

## The Shrinkage Estimator

@@

## The NOVELIST Estimator

@@

## Alternative Covariance Estimators
